%!TEX root = ../dokumentation.tex

\pagestyle{plain}

\iflang{en}{%
\addchap{\langabstractEN} % Text für Überschrift

In the modern world of IT and Artifical Intelligence data gains more and more importance. Those data is needed for training Machine Learning systems as well as Business Analytics for better decision making. Thereby in the last years there was a rising demand of real-time analytics instead of common Big Data Analytics, which needs far more time.

Therefore IBM Research prototyped a system, which combines the fast transactional processing with analytics processing. Such a system is called ``Hybrid Transactional and Analytical Processing''. For enabling both - fast transactions as well as analysis on Big Data - the data needs to be in different forms, which means, that the data has to be transformed. In IBMs prototype called ``Wildfire'' there are two stages for that - the groomer and the postgroomer.

In this report first Wildfire and its base technologies will be described and explained. Further there will be described some performance tests with the Wildfire postgroomer. To increase the performance and availability of that, during the described project Wildfire should be setup in a Kubernetes Cluster. The explanation of Kubernetes and its functionality will also be part of this report.

The third part will be about another big movement in the IT - the move to the Cloud. For more efficiency many companies move from physical devices to Cloud devices - so does IBM Research for concentrating its computational power in the Cloud. In this report this Cloud system will be evaluated as replacement for running the Wildfire postgroomer in it instead of running it on physical devices located in the Research Lab in Almaden.

}